\begin{thebibliography}{}

  \bibitem[Bishop 07]{bishop}
  Bishop,~C.~M.: {\em Pattern Recognition and Machine Learning (Information Science and Statistics)}, Springer, 1 edition (2007)
  
  \bibitem[Caplan 15]{caplan2015risk}
  Caplan,~J.~M.et al.: Risk terrain modeling for spatial risk assessment, {\em Cityscape}, Vol.~17, No.~1, pp. 7--16 (2015)
  
  \bibitem[CDPH 24]{ChicagoDataPortal}
  Chicago Department of Public Health. (2024), \url{https://data.cityofchicago.org/}
  
  \bibitem[Chainey 08]{chainey2008utility}
  Chainey,~S. et al.: The utility of hotspot mapping for predicting spatial patterns of crime, {\em Security journal}, Vol.~21, pp. 4--28 (2008)
  
  \bibitem[DeLong 88]{DeLong}
  DeLong,~E.~R., et al.: Comparing the Areas under Two or More Correlated Receiver Operating Characteristic Curves: A Nonparametric Approach, {\em Biometrics}, Vol.~44, No.~3, pp. 837--845 (1988)
  
  \bibitem[Hastie 01]{esl}
  Hastie,~T., et al.: {\em The Elements of Statistical Learning}, Springer Series in Statistics, Springer New York Inc., New York, NY, USA (2001)
  
  \bibitem[Hilbe 11]{Hilbe_2011}
  Hilbe,~J.~M.: {\em Negative Binomial Regression}, Cambridge University Press, 2 edition (2011)

  \bibitem[Yeo 00]{yeo}
  I. Yeo , R. Johnson: A new family of power transformations to improve normality or symmetry {\em Biometrika}, vol. 87, pp. 954--959, (2000)

  \bibitem[James 23]{islp}
  James,~G., et al.: {\em An Introduction to Statistical Learning with Applications in Python}, Springer Texts in Statistics, Springer, Cham (2023)
  
  \bibitem[Jordahl 20]{geopandas}
  Jordahl,~K., et al.: geopandas/geopandas: v0.8.1 (2020)
  
  \bibitem[Joshi 20]{joshi2020considerationsdevelopingpredictivemodels}
  Joshi,~C. et al.: Considerations for developing predictive models of crime and new methods for measuring their accuracy (2020)
  
  \bibitem[Nelder 72]{poisson}
  Nelder,~J.~A., Wedderburn,~R.~W.~M.: Generalized Linear Models, {\em Journal of the Royal Statistical Society. Series A (General)}, Vol. 135, No.~3, pp. 370--384 (1972)
  
  \bibitem[Pedregosa 11]{scikit-learn}
  Pedregosa,~F. et al.: Scikit-learn: Machine Learning in {P}ython, {\em Journal of Machine Learning Research}, Vol.~12, pp. 2825--2830 (2011)
  
  \bibitem[Tibshirani 96]{Lasso}
  Tibshirani,~R.: Regression shrinkage and selection via the lasso, {\em Journal of the Royal Statistical Society Series B: Statistical Methodology}, Vol.~58, No.~1, pp. 267--288 (1996)
  
  \bibitem[守山 22]{犯罪予測}
  守山正：犯罪予測 : AIによる分析, 成文堂 (2022)
  
  \bibitem[大山 17]{地理的犯罪予測研究の潮流}
  大山智也 et al.：地理的犯罪予測研究の潮流, GIS-理論と応用, Vol.~25, No.~1, pp. 33--43 (2017)
  
  \bibitem[大山 20]{大山智也2020日本}
  大山智也：日本における地理的犯罪予測手法の開発に関する研究 (2020)
  
  \end{thebibliography}
  